animbook: Visualizing Changes in Performance Measures and Demographic Affiliations using Animation

### 2025-07-11 response_to_review.qmd

*b) Beginning of Section 5. Please delete the letters “R. E.” from the reference of Mayer and Moreno (2002).*

Response: All referencing are automated and the style is consistent with the R journal style so we have no control over this.

*c) Page 13. First paragraph, 3rd and 4rth lines probably have a typo (“…and japan”).*

Response: "japan" is one of the variables in the osiris data. We have changed the text so that this is clearer.

@@

*4. The description you give for Figure 10 helps the reader understand the meaning of this plot. But, in the example in the R package with the aeles dataset, things are not so obvious. There are many observations that mask the visibility of the points.Also, what do the X and Y mean?*

Response: XXX We have fixed the example on the package website and provide more documentation about the animation.

@@

Response: Fixed

### *Code*

*I did not find the commands in the package very user-friendly. For instance, to produce a plot I must go through many functions, prior to typing the plot to appear. The example in the aeles dataset is such a case. I need to type 4 commands in order to see a plot, which I repeat, cannot understand, nor interpret easily. I would prefer a function that does all this preprocessing and plots the data. Legends are missing, and in my opinion, the help files are not very helpful for someone who wants to use this package easily, to visualize their data.*

Response: This was a design choice for transparency so the user can see the steps. We have updated the web page to make the steps clearer, and also added a single function that does all the steps. XXX

### 2025-07-11 animbook-journal.Rmd
and japan comment
ID and grouping comment finished

In the data structure, there are requirements that must be followed for reproducing the animation. First, the dataset needs to be in a `tidy data` format (@tidy-data). The data then must have at least ID and time variables, in addition to the measured variables, which would usually be numeric but can also be categorical as well. The ID variable indicates the individual, which is followed over time, such as the company name. There may also be a grouping variable, such as the country where the company is registered (United States and Japan).

@@

The Osiris data presented in this section was acquired from Bureau van Dijk (@bvd), compiling information on a total of 122,318 companies. It was subsequently subsetted for the 2021 report, consisting of 1000 companies with 94 variables. The dataset included in the package focuses on 790 companies, spanning from 2006 to 2018. The variables in this dataset include year, ID, country, sales, and japan.

>>>>

In the data structure, there are requirements that must be followed for reproducing the animation. First, the dataset needs to be in a `tidy data` format (@tidy-data). The data then must have at least ID and time variables, in addition to the measured variables, which would usually be numeric but can also be categorical as well. The ID variable indicates the individual, which is followed over time, such as the company name. There may also be a grouping variable, such as the country where the company is registered (United States and Japan), which would be used to color points for group comparison.

@@

The Osiris data presented in this section was acquired from Bureau van Dijk (@bvd), compiling information on a total of 122,318 companies. It was subsequently subsetted for the 2021 report, consisting of 1000 companies with 94 variables. The dataset included in the package focuses on 790 companies, spanning from 2006 to 2018. The variables in this dataset include year, ID, country, sales, and the binary variable called japan.
